---
title: "Introduction to robvis, a visualisation tool for risk-of-bias assessments"
author: ""
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Introduction to robvis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  fig.width = 8,
  fig.height = 2.41)
  library(ggplot2)
  library(robvis)
```
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot by the tool used.

Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2

### Common structure of risk-of-bias assessment output (usually in Excel)
```{r headrob}
knitr::kable(data_rob)
```


### RoB2.0 tool for randomised controlled trials
```{r rob2summary}
rob_summary(data_rob, tool = "ROB2", save = "No")
```

### ROBINS-I tool for non-randomised studies of interventions
```{r robinssummary}
rob_summary(data_robins, tool = "ROBINS-I", save = "No")
```

### QUADAS-2 for diagnostic test accuracy studies
```{r quadassummary}
rob_summary(data_quadas, tool = "QUADAS-2", save = "No")
```
