---
title: "Working with metafor"
author: "Luke A McGuinness"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: yes
    toc_depth: 4
vignette: |
  %\VignetteIndexEntry{Working with metafor} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`robvis` now provides some functionality to work with the results of meta-analyses performed using the [`metafor` package](https://wviechtb.github.io/metafor/index.html).

First let's load the relevant packages and define our datasets:

```{r setup, message=FALSE, warning=FALSE}
library(robvis)
library(metafor)

# Define your studies, using nine studies from the of the BCG dataset included in the metafor package
data_bcg <- metadat::dat.bcg[c(1:9),]

data_bcg

# Import the example RoB2 dataset included with robvis
data_rob <- robvis::data_rob2

data_rob

```

## Perform the meta-analysis

Let's now perform a simple random-effects meta-analysis using `metafor::rma()`:

```{r}
# Calculate effect estimates and sampling variances for each study
data_bcg <-
  metafor::escalc(
    measure = "RR",
    ai = tpos,
    bi = tneg,
    ci = cpos,
    di = cneg,
    data = data_bcg
  )

# Perform the meta-analysis
res <- metafor::rma(yi,
                    vi,
                    data = data_bcg,
                    slab = paste("Study", 1:9))

# Explore the results
res
```


Note, it is important that the `slab` variable defined in `metafor::rma()` above and the `Study` variable of the risk-of-bias dataset are identical, as the data is merged on the basis of these variables in the next section. Here I have just used "Study 1" -> "Study 9", but another good option is author name and year:


```{r}
data_rob$Study

res$slab

```

## Risk of bias plots

### Appending risk-of-bias plots to forest plots

Having performed the meta-analysis, you can now append a risk-of-bias traffic-light plot onto the standard output from `metafor::forest()` by passing the results object (`res`) and the risk-of-bias dataset (`data_rob`) to `rob_append_to_forest()`:

```{r, fig.width=10}
rob_append_to_forest(res, data_rob)

```

### Extract and append weights

Alternatively, you can extract the weights assigned to each study in the meta-analysis and append them to the risk-of-bias dataset. This weighted risk-of-bias dataset can then be passed to `rob_summary()` where the `weighted` argument is set to `TRUE` to produce summary plots which show the amount of statistical information, rather than the number of studies, that is at each level of risk of bias. 

```{r, out.height=400}
# Extract the weights assigned to each study from the meta-analysis and append them to the risk-of-bias dataset
data_rob <- rob_append_weights(data_rob, res)

# Pass this weighted dataset to the rob_summary() function, and set weighted = TRUE
rob_summary(data_rob, tool = "ROB2", weighted = TRUE)

# Compare this to the un-weighted bar plots (weighted = FALSE)
rob_summary(data_rob, tool = "ROB2", weighted = FALSE)
```




