---
title: "Working with metafor"
author: "Luke A McGuinness"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: yes
    toc_depth: 4
vignette: |
  %\VignetteIndexEntry{Working with metafor} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`robvis` now provides some functionality to work with the results of meta-analyses performed using the [`metafor` package](https://wviechtb.github.io/metafor/index.html).

First let's load the relevant packages and define our datasets:

```{r setup, message=FALSE, warning=FALSE}
library(robvis)
library(metafor)
library(dplyr)

# Define your studies, using the BCG dataset included in the metadat package
dat_bcg <- metadat::dat.bcg

glimpse(dat_bcg)

# Create some example data for ROB2 using rob_dummy(), and add it to the BCG
# data.
# We don't need a "Study" column for this example, so we set `study = FALSE`

dat_rob <- rob_dummy(13, 
                     "ROB2",
                     study = FALSE)

dat_analysis <- cbind(dat_bcg, dat_rob)

glimpse(dat_analysis)
```

Now each row in the dataset contains a single numerical result and it's corresponding risk-of-bias assessment.

## Perform the meta-analysis

Let's now perform a simple random-effects meta-analysis using `metafor::rma()`:

```{r}
# Calculate effect estimates and sampling variances for each study
dat_analysis <-
  metafor::escalc(
    measure = "RR",
    ai = tpos,
    bi = tneg,
    ci = cpos,
    di = cneg,
    data = dat_analysis
  )

# Perform the meta-analysis
res <- metafor::rma(yi,
                    vi,
                    data = dat_analysis,
                    slab = paste(author, year))

# Explore the results
res
```

## Create paired forest plot

Having performed the meta-analysis, you can now append a risk-of-bias traffic-light plot onto the standard output from `metafor::forest()` by simply passing the results object (`res`) to `rob_forest()`:

```{r, fig.width=10}
rob_forest(res, rob_tool = "ROB2")
```

This function is designed to make it as easy as possible to substitute `rob_forest()` for `metafor::forest()`.

## Risk of bias due to missing evidence 

<!-- ### Extract and append weights -->

<!-- Alternatively, you can extract the weights assigned to each study in the meta-analysis and append them to the risk-of-bias dataset. This weighted risk-of-bias dataset can then be passed to `rob_summary()` where the `weighted` argument is set to `TRUE` to produce summary plots which show the amount of statistical information, rather than the number of studies, that is at each level of risk of bias. -->

<!-- ```{r, out.height=400} -->
<!-- # Extract the weights assigned to each study from the meta-analysis and append them to the risk-of-bias dataset -->
<!-- data_rob <- rob_append_weights(data_rob, res) -->

<!-- # Pass this weighted dataset to the rob_summary() function, and set weighted = TRUE -->
<!-- rob_summary(data_rob, tool = "ROB2", weighted = TRUE) -->

<!-- # Compare this to the un-weighted bar plots (weighted = FALSE) -->
<!-- rob_summary(data_rob, tool = "ROB2", weighted = FALSE) -->
<!-- ``` -->




